Human Factors Influencing Visual Statistical Inference

### 2015-05-17 sociology_paper.tex
typos

%\subsection{Individual Skill or Ability} 
\item{\bf Individual Skill or Ability:} Each person may have different  aptitude for reading statistical plots, and their visual skill sets might be differently developed. We \hh{We can evaluate the effect of individuals' skills and abilities}  by letting multiple subjects evaluate the same lineups, which allows us to estimate, if some subjects consistently detect the actual data plot more often than others.  
 %For example, in a controlled experimental study \citet{zhao:2012}  noticed that some people spent a lot of time to decide no matter whether the lineup is difficult or easy while some simply glanced at lineups to make a decision. This influences the response of the observer. Also subject specific variation in the power of visual test is observed in \cite{majumder:2013}. 
\end{itemize}

>>>>

%\subsection{Individual Skill or Ability} 
\item{\bf Individual Skill or Ability:} Each person may have different  aptitude for reading statistical plots, and their visual skill sets might be differently developed.  \hh{We can evaluate the effect of individuals' skills and abilities}  by letting multiple subjects evaluate the same lineups, which allows us to estimate, if some subjects consistently detect the actual data plot more often than others.  
 %For example, in a controlled experimental study \citet{zhao:2012}  noticed that some people spent a lot of time to decide no matter whether the lineup is difficult or easy while some simply glanced at lineups to make a decision. This influences the response of the observer. Also subject specific variation in the power of visual test is observed in \cite{majumder:2013}. 
\end{itemize}
